%-----------PROJECTS-----------%
\section{Projects}
\resumeSubHeadingListStart

    \resumeProjectHeading
    {\textbf{Adaptive Traffic Signal Control System} $|$ \emph{Python, Convolutional Neural Networks, Fuzzy Logic}}{}
    \resumeItemListStart
        \resumeItem{Optimized traffic signal timings by integrating a CNN model for accurate traffic flow detection, improving the precision of traffic data collected.}
        \resumeItem{Utilized fuzzy logic for adaptive decision-making, creating a dynamic system that responds to real-time traffic conditions effectively.}
        \resumeItem{Developed a scalable and resource-efficient solution, ensuring the system remains lightweight and easily deployable on standard infrastructure.}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{Network Intrusion Detection System} $|$ \emph{Python, Random Forest, Gradient Boosting, Ensemble Learning}}{}
    \resumeItemListStart
        \resumeItem{Developed a high-performance IDS using an ensemble learning approach, integrating Random Forest, Gradient Boosting and Stacking to achieve 95.2\% accuracy in detecting anomalies and reducing false positives.}
        \resumeItem{Performed advanced data pre-processing techniques, including feature encoding, outlier detection and model benchmarking based on performance metrics, to enhance data quality.}
        \resumeItem{Designed a real-time anomaly detection system for adaptability to emerging threats and potential integration into enterprise, IoT and cloud environments.}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{Polycon | Icon Pack Maker for Android} $|$ \emph{Kotlin, Jetpack Compose}}{}
    \resumeItemListStart
        \resumeItem{Developed a highly customizable Android tool for curating and generating personalized icon packs for their preferred Android launchers.}
        \resumeItem{Engineered a sleek, Material Design-inspired dashboard incorporating responsive UI elements whilst ensuring seamless integration and compatibility with a range of devices.}
        \resumeItem{Optimized application performance for a lightweight, user-friendly experience for all platforms.}
    \resumeItemListEnd

\resumeSubHeadingListEnd